Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-14 doc/JFLA2022/paper.tex
add Simpson's set theory to ancestry graph

\begin{scope}[xshift=-6cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,left of=goedel, node distance=2.2cm] (pock) { Pocklington };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2.5cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=2cm] (cantor) { Cantor };
\end{scope}

\begin{scope}[yshift=-1cm,xshift=0.45cm]
  \node[rectangle, draw=black,fill=gray!30,minimum height=0.5cm,minimum width=1.5cm] (paramcoq) { Paramcoq };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=paramcoq, node distance=2cm] (mathcomp) { MathComp };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,left of=paramcoq, node distance=4.5cm] (equations) { Equations };
\end{scope}

@@

\draw[->,dotted] (additions.south) -- (chains.north) ;
\draw[->,dotted] (goedel) -- (goedelcc) ;
\draw[->,dotted] (goedel) -- (hydras.north west) ;
\draw[->,dotted] (cantor) -- (hydras.north east) ;
\draw[->,dotted] (cantor.south) -- (gaia.north west) ;
\draw[->,dotted] (pock) -- (pockcc) ;

@@

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages. Dotted boxes represent historical Coq contributions, while regular boxes represent maintained Coq packages. Dark grey packages are maintained in the \Hydras GitHub repository, while light grey packages are maintained in other \community repositories. Dotted lines represent Coq code ancestry, while regular lines represent direct code dependencies.}
  \label{fig:genealogy}
\end{figure}

>>>>

\begin{scope}[xshift=-6cm]
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm] (goedel) { Goedel };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,left of=goedel, node distance=2.2cm] (pock) { Pocklington };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=goedel, node distance=2.5cm] (additions) { Additions };
\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=additions, node distance=2cm] (cantor) { Cantor };

\node[rectangle, dotted,draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=cantor, node distance=3.2cm] (cats) { Categories in ZFC };
\end{scope}

\begin{scope}[yshift=-1cm,xshift=0.45cm]
  \node[rectangle, draw=black,fill=gray!30,minimum height=0.5cm,minimum width=1.5cm] (paramcoq) { Paramcoq };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,right of=paramcoq, node distance=2.5cm] (mathcomp) { MathComp };
\node[rectangle, draw=black,minimum height=0.5cm,minimum width=1.5cm,node distance=2cm,left of=paramcoq, node distance=4.5cm] (equations) { Equations };
\end{scope}

@@

\draw[->,dotted] (additions.south) -- (chains.north) ;
\draw[->,dotted] (goedel) -- (goedelcc) ;
\draw[->,dotted] (goedel) -- (hydras.north west) ;
\draw[->,dotted] (cantor) -- (hydras.north east) ;
\draw[->,dotted] (cantor.south) -- (gaia.north west) ;
\draw[->,dotted] (pock) -- (pockcc) ;
\draw[->,dotted] ([xshift=2.1cm]cats) -- (gaia) ;

@@

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages. Dotted boxes represent historical Coq contributions, while regular boxes represent maintained Coq packages. Dark gray packages are maintained in the \Hydras GitHub repository, while light gray packages are maintained in other \community repositories. Dotted lines represent Coq code ancestry, while regular lines represent direct code dependencies.}
  \label{fig:genealogy}
\end{figure}
